---
title: "Peer assessment 1 submission - Reproducible Research"
output: html_document
---


##Loading and preprocessing the data

First of all, we need to start with the data tune-up.  This is the code for it: 

*Code:*

```{r, echo=TRUE}
rawData <- read.csv("activity.csv")

complCas <- complete.cases(rawData)

procData <- rawData[complCas, ]
```


##What is mean total number of steps taken per day?

As per requested, the mean and median of the total number of steps taken per day are 10766.1 and 10765, respectively. 


*Code:*

```{r, echo=TRUE}
uniqueCasesDate <- unique(procData$date)

dailySteps <- c()

meanDailySteps <- c()

for (i in 1:length(uniqueCasesDate)){
  
  dailySteps[i] <- sum(procData[which(procData$date == uniqueCasesDate[i]),"steps"])
  meanDailySteps[i] <- sum(procData[which(procData$date == uniqueCasesDate[i]),"steps"])/length(procData[which(procData$date == uniqueCasesDate[i]),"steps"])
}

complData <- data.frame(uniqueCasesDate, meanDailySteps)



meanSteps <- sum(dailySteps)/length(dailySteps)
medianSteps <- median(dailySteps)

print(paste("- The mean of the daily steps is ", meanSteps, sep = ""))
print("")
print(paste("- The median of the daily steps is ", medianSteps, sep = ""))

```


Here is the histogram for the total number of steps taken each day: 

```{r, echo=FALSE}
hist(dailySteps)
```

##What is the average daily activity pattern?

The interval with the most average steps is 835. 






*Code:*

```{r, echo=TRUE}

uniqueCasesInter <- unique(procData$interval)

interSteps <- c()

for (i in 1:length(uniqueCasesInter)){
  
  interSteps[i] <- mean(procData[which(procData$interval == uniqueCasesInter[i]),"steps"])#/length(procData[which(procData$interval == uniqueCasesInter[i]),"steps"])
}




maxInterval <- uniqueCasesInter[which.max(interSteps)]

print(paste("- The interval with the most average steps is ", maxInterval, sep = ""))



```


This is the times series plot for the average number of steps taken, averaged across all days Vs. 5-minute interval:

```{r, echo=FALSE}
plot(uniqueCasesInter, interSteps, type = "l")
```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
